### 2013-02-26 LaTeX/RhodiumIntro.tex
added notes

Two schools of thought on civil war and economic development: ``war renewal'' and ``war ruin'' schools

>>>>

Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet. When should we expect to see the adverse effects of civil war manifest themselves in terms of lower economic growth?

Cases apart from Mexico:
Pakistan - NWFP
India
Israel
Russia - Chechnya
Columbia - FAARC
